### 2019-02-22 sections/introduction.tex
Added cite to mTasks temperature paper
Hide fixme from intro

Users can work together in a number of ways, and this is reflected in \TOP by task compositions.
There is sequential composition, parallel composition, and choice.
Users need to communicate in order to engage in these forms of collaboration.
This is reflected in \TOP by three kinds of communication mechanisms.
There is data flow \emph{alongside} control flow, where the result of a task is passed onto the next.
There is data flow \emph{across} control flow, where information is shared between multiple tasks.
Finally, there is communication with the \emph{outside} world, where information is entered into the system via input events.
\fixme{Should this be mentioned earlier?}
The end points where the outside world interacts with \TOP applications are called editors.
In generated applications, editors can take many forms, like input fields, selection boxes, or map widgets.

@@

\MTASKS is a subset of \ITASKS,
focussing on \IOT devices and deployment on micro controllers.
It has been used to control home thermostats and other home automation applications \fixme{cite}.

>>>>

Users can work together in a number of ways, and this is reflected in \TOP by task compositions.
There is sequential composition, parallel composition, and choice.
Users need to communicate in order to engage in these forms of collaboration.
This is reflected in \TOP by three kinds of communication mechanisms.
There is data flow \emph{alongside} control flow, where the result of a task is passed onto the next.
There is data flow \emph{across} control flow, where information is shared between multiple tasks.
Finally, there is communication with the \emph{outside} world, where information is entered into the system via input events.
%\fixme{Should this be mentioned earlier?}
The end points where the outside world interacts with \TOP applications are called editors.
In generated applications, editors can take many forms, like input fields, selection boxes, or map widgets.

@@

\MTASKS is a subset of \ITASKS,
focussing on \IOT devices and deployment on micro controllers.
It has been used to control home thermostats and other home automation applications \cite{koopman2018task}.
